Refunctionalization of Abstract Abstract Machines (Functional Pearl)

### 2018-07-05 paper/paper.tex
typos

  \item In the second case, an atomic expression @ae@ sits on the control position of the
    state. Here, the value of @ae@ is being returned to its caller.
    In order to accomplish this, we dereference the continuation address @kaddr@ and obtain 
    a set of continuations @conts@. For each continuation in the set, we construct an 
    environment based on the environment @env_f@ of the frame, and bind @x@ to a newly 
    created binding address @baddr@. We must also update the store with @baddr@ and the 
    values that @ae@ represents. In every generated state, the control becomes the expression 
    @e@ in the frame, and as we can tell from the name, the continuation address @f_kaddr@ 
    also comes from the frame.
\end{itemize}

@@

Given a collection of elements of type @T@, an initial accumulator of type @Ans@,
a function @k@ that works on elements of type @T@, @nd@ chooses an element in
the collection and applies @k@ to it iteratively, and accumulates the value that
returned from @k@ when recurring on the rest of the collection. Eventually, @nd@
returns the accumulated value @acc@ when there is no element in the collection.
The latest accumulated cache @acc.cache@ is exposed to @k@ when applied.

>>>>

  \item In the second case, an atomic expression @ae@ sits on the control position of the
    state. Here, the values of @ae@ is being returned to its caller.
    In order to accomplish this, we dereference the continuation address @kaddr@ and obtain 
    a set of continuations @conts@. For each continuation in the set, we construct an 
    environment based on the environment @env_f@ of the frame, and bind @x@ to a newly 
    created binding address @baddr@. We must also update the store with @baddr@ and the 
    values that @ae@ represents. In every generated state, the control becomes the expression 
    @e@ in the frame, and as we can tell from the name, the continuation address @f_kaddr@ 
    also comes from the frame.
\end{itemize}

@@

Given a collection of elements of type @T@, an initial accumulator of type @Ans@,
a function @k@ that works on elements of type @T@, @nd@ chooses an element in
the collection and applies @k@ to it iteratively, and accumulates the values that
returned from @k@ when recurring on the rest of the collection. Eventually, @nd@
returns the accumulated value @acc@ when there is no element in the collection.
The latest accumulated cache @acc.cache@ is exposed to @k@ when applied.
